Laplacian envelope

### 2020-07-07 Notes/laplace.tex
moved model creation

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\usepackage{mathtools}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}

@@

We model a synapse as having $M$ internal states.
The synaptic weight depends deterministically on the state, given by the $M$-element column vector $\w$.
We denote the probability distribution across these states by the row vector $\pr(t)$.
We denote a column vector of ones by $\onev$, so the normalisation condition is $\pr(t)\onev=1$.

When the synapse is subjected to a plasticity event the internal state will change stochastically, described by the matrices $\M^\mu$ whose $i,j$ elements are the transition probabilities from state $i$ to state $j$, 
and \(\mu\) labels the diffrerent types of plasticity event.
Potentiating events have \(\mu=\)pot, depressing events have \(\mu=\)dep.
We also use the notation
%
\begin{equation*}
  (-1)^\mu = 
    \begin{cases}
       1, & \mu = \text{pot}, \\
      -1, & \mu = \text{dep}.
    \end{cases}
\end{equation*}
%
The matrices $\M^\mu$ are transition matrices of discrete time Markov processes.
Their elements must satisfy the following constraints
%
\begin{equation}\label{eq:constr}
  \M^\mu_{ij} \geq 0 
    \quad \forall \; \mu, i, j, \qquad
  \sum_j \M^\mu_{ij} = 1
    \quad \forall \; \mu, i.
\end{equation}
%
The upper bounds $\M^\mu_{ij} \leq 1$ follow automatically from these.

If we treat the off diagonal elements as the independent degrees of freedom, with the off diagonal elements determined by the row sum constraints (second column of \eqref{eq:constr}), the constraints are
%
\begin{equation}\label{eq:constri}
  \M^\mu_{i j} \geq 0
    \quad \forall \; \mu, i, j : i \neq j, \qquad
  \sum_{j : j\neq i} \M^\mu_{ij} \leq 1
    \quad \forall \; \mu, i.
\end{equation}
%
The second of these will be referred to as the ``diagonal'' constraint.

Given a sequence of plasticity events at times $t_1,t_2,t_3,\ldots$, the probability distribution across the internal states at time $t_n$ is
%
\begin{equation}\label{eq:plastseq}
  \pr(t_n) = \pr(t_0)  \M\pot \M\dep \M\dep \M\pot \M\dep \M\pot \M\pot \M\dep \ldots \M\pot .
\end{equation}
%
If the probability of a given plasticity event being potentiating/depressing is $f^\mu$, the probability of the sequence above (conditioned on the number of events) is given by $f\pot f\dep f\dep f\pot f\dep f\pot f\pot f\dep \ldots f\pot$.

@@

If the plasticity events occur at Poisson rate $r$, the probability of $n$ events occurring in time $t$ is given by a Poisson distribution with mean $rt$.
If we marginalise over $n$ as well
%
\begin{equation}\label{eq:plastseqav}
\begin{aligned}
  P(\text{state}=i,t \mid \text{pot/dep},0)
    &= \sum_n \frac{(rt)^n}{n!} \e^{-rt} \eq \M\potdep (f\pot\M\pot+f\dep\M\dep)^n \\
    &= \brk{ \eq \M\potdep\, \e^{rt(f\pot\M\pot+f\dep\M\dep-\I) } }_i,
\end{aligned}
\end{equation}
%
where $\eq$ is the steady state distribution of the continuous time transition matrix that appears in the exponential:
%
\begin{equation}\label{eq:eq}
  \eq\frg = 0,
  \qquad\text{where}\quad
  \frg = \sum_\alpha f^\mu \M^\mu - \I
    = f\pot\M\pot + f\dep\M\dep - \I.
\end{equation}
%

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \e^{rt\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \e^{rt\frg} \w .
\end{aligned}
\end{equation}
%
Combining these allows us to write the numerator of \eqref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= N \eq \enc \, \e^{rt \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\mu (-1)^\mu f^\mu (\M^\mu - \I)
    = f\pot(\M\pot-\I)-f\dep(\M\dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{rt\frg}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with $f\pot=f\dep$ or $\eq_+=\eq_-$.
We can perform the maximisation in two steps.
First maximise the numerator at fixed $\eq\w$.
Then maximise the ratio \wrt $\eq\w$.
This will allow us to ignore the denominator until the very end.

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s\I +\onev\pib -\MM)\inv,
\end{equation}
%
where $\pib$ is an arbitrary row vector satisfying $\pib\onev = \frac{1}{\tau_0} \neq 0$.
This reduces to the fundamental matrix at $s=0$.
We can see that $\onev$ is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau_0}{1+s\tau_0}\onev.
\end{equation}
%
Suppose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\pib$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\pib_k} = -(\mathbf{a}\fund(s)\onev) \fund_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

Then we also define
%
\begin{equation}\label{eq:lfptb}
  \fptb(s) = (\onem\fund\dg(s)-\fund(s))\D,
  \qquad
  \fptb_{ij}(s) = \frac{\fund_{jj}(s)-\fund_{ij}(s)}{\eq_j}.
\end{equation}
%
This reduces to the first passage time matrix at $s=0$, but at other $s$ there is (probably) no relation.

Using the exact same proof as in the case $s=0$, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau}{1+s\tau}$.
We can the define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s)\eq_j \prn{\frac{1\pm\w_j}{2}} =  \sum_{j\in\pm} \fptb_{ij}(s)\eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etw_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w_j
    = \eta^+_i(s) - \eta^-_i(s) =2\eta^+_i(s) - \eta(s) =\eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\etw_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
These quantities can still be used when $\w$ takes more than two values.

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact} (ignoring the denominator)
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }{ \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \enc_{ij} (\etw_{i}(s) - \etw_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\usepackage{mathtools}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arow}{\boldsymbol{\xi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}

@@

We model a synapse as having $M$ internal states.
The synaptic weight depends deterministically on the state, given by the $M$-element column vector $\w$.
We denote the probability distribution across these states by the row vector $\pr(t)$.
We denote a column vector of ones by $\onev$, so the normalisation condition is $\pr(t) \, \onev=1$.

When the synapse is subjected to a plasticity event the internal state will change stochastically, described by the matrices $\M^xn  $ whose $i,j$ elements are the transition probabilities from state $i$ to state $j$, 
and \(\nu \) labels the diffrerent types of plasticity event.
Potentiating events have \(\nu=\)pot, depressing events have \(\nu=\)dep.
We also use the notation
%
\begin{equation*}
  (-1)^\nu = 
    \begin{cases}
       1, & \nu = \text{pot}, \\
      -1, & \nu = \text{dep}.
    \end{cases}
\end{equation*}
%
The matrices $\M^\nu$ are transition matrices of discrete time Markov processes.
Their elements must satisfy the following constraints
%
\begin{equation}\label{eq:constr}
  \M^\nu_{ij} \geq 0 
    \quad \forall \; \nu, i, j, \qquad
  \sum_j \M^\nu_{ij} = 1
    \quad \forall \; \nu, i.
\end{equation}
%
The upper bounds $\M^\nu_{ij} \leq 1$ follow automatically from these.

If we treat the off diagonal elements as the independent degrees of freedom, with the off diagonal elements determined by the row sum constraints (second column of \eqref{eq:constr}), the constraints are
%
\begin{equation}\label{eq:constri}
  \M^\nu_{i j} \geq 0
    \quad \forall \; \nu, i, j : i \neq j, \qquad
  \sum_{j : j\neq i} \M^\nu_{ij} \leq 1
    \quad \forall \; \nu, i.
\end{equation}
%
The second of these will be referred to as the ``diagonal'' constraint.

Given a sequence of plasticity events at times $t_1,t_2,t_3,\ldots$, the probability distribution across the internal states at time $t_n$, 
mariginalising over states at earlier times, is
%
\begin{equation}\label{eq:plastseq}
  \pr(t_n) = \pr(t_0)  \M\pot \M\dep \M\dep \M\pot \M\dep \M\pot \M\pot \M\dep \ldots \M\pot .
\end{equation}
%
If the probability of a given plasticity event being potentiating/depressing is $f\potdep$, the probability of the sequence above (conditioned on the number of events) is given by $f\pot f\dep f\dep f\pot f\dep f\pot f\pot f\dep \ldots f\pot$.

@@

If the plasticity events occur at Poisson rate $r$, the probability of $n$ events occurring in time $t$ is given by a Poisson distribution with mean $rt$.
If we marginalise over $n$ as well
%
\begin{equation}\label{eq:plastseqav}
\begin{aligned}
  P(\text{state}=i,t \mid \text{pot/dep},0)
    &= \sum_n \frac{(rt)^n}{n!} \e^{-rt} \eq \M\potdep (f\pot\M\pot+f\dep\M\dep)^n \\
    &= \brk{ \eq \M\potdep\, \e^{rt(f\pot\M\pot+f\dep\M\dep-\I) } }_i,
\end{aligned}
\end{equation}
%
where $\eq$ is the steady state distribution of the continuous time transition matrix that appears in the exponential:
%
\begin{equation}\label{eq:eq}
  \eq\frg = 0,
  \qquad\text{where}\quad
  \frg = \sum_\nu f^\nu \M^\nu - \I
    = f\pot\M\pot + f\dep\M\dep - \I.
\end{equation}
%

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \e^{rt\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \e^{rt\frg} \w .
\end{aligned}
\end{equation}
%
Combining these allows us to write the numerator of \eqref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= N \eq \enc \, \e^{rt \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu f^\nu (\M^\nu - \I)
    = f\pot(\M\pot-\I)-f\dep(\M\dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{rt\frg}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with $f\pot=f\dep$ or $\eq_+=\eq_-$.
We can perform the maximisation in two steps.
First maximise the numerator at fixed $\eq\w$.
Then maximise the ratio \wrt $\eq\w$.
This will allow us to ignore the denominator until the very end.

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s \I + \onev \arow -\MM)\inv,
\end{equation}
%
where $\arow$ is an arbitrary row vector satisfying $\arow \onev = \frac{1}{\tau_0} \neq 0$.
This reduces to the fundamental matrix at $s=0$.
We can see that $\onev$ is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau_0}{1+s\tau_0}\onev.
\end{equation}
%
Suppose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\arow$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\arow_k} = -(\mathbf{a}\fund(s)\onev) \fund_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

Then we also define
%
\begin{equation}\label{eq:lfptb}
  \fptb(s) = (\onem \fund\dg(s)-\fund(s))\D,
  \qquad
  \fptb_{ij}(s) = \frac{\fund_{jj}(s)-\fund_{ij}(s)}{\eq_j}.
\end{equation}
%
This reduces to the first passage time matrix at $s=0$, but at other $s$ there is (probably) no relation.

Using the exact same proof as in the case $s=0$, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau}{1+s\tau}$.
We can then define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s) \eq_j \prn{\frac{1 \pm \w_j}{2}} 
      =  \sum_{j\in \pm} \fptb_{ij}(s) \eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etw_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w_j
    = \eta^+_i(s) - \eta^-_i(s) 
    = 2\eta^+_i(s) - \eta(s) 
    = \eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\etw_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
The $\etw_i(s)$ can still be used when $\w$ takes more than two values.

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }
                                { \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \enc_{ij} (\etw_{i}(s) - \etw_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.
